|

### 2021-02-13 manuscript/article.Rmd
small changes to author summary

\noindent Diseases transmitted by the \textit{Aedes aegypti} mosquito, such as
chikungunya, dengue, yellow fever, and Zika, continue to kill thousands of
people per year. As there is no safe vaccine for many of these infections,
insecticide spraying and breeding site cleaning are the best means to fight the
mosquito. In several developing countries, which host the majority of cases of
\textit{A. aegypti} infections, anti-mosquito campaigns are carried out
inconsistently, thus it is crucial to find ways to improve the productivity of
healthcare workers in charge of these tasks. We designed a randomised field
experiment that provided individual and collective financial incentives to
healthcare agents in a Brazilian city and tested the effect of monetary rewards
on their productivity and on the number of dengue hospitalisations. We find
that financial bonuses improved the number of cleaned breeding sites in both
treatment groups (individual and team incentives) and that the collective
treatment also improved larvae extermination. The impact of our treatment on
city-level hospitalisations was not consistent across all specifications. In
sum, financial incentives may be used to boost field productivity in
anti-\textit{A. aegypti} programmes, but we suggest that further research is
required to evaluate how healthcare worker productivy relates to aggregate
disease outcomes.

>>>>

\noindent Diseases transmitted by the \textit{Aedes aegypti} mosquito, such as
chikungunya, dengue, yellow fever, and Zika, continue to kill thousands of
people per year. As there are no safe vaccines for many of these infections,
insecticide spraying and breeding site cleaning are the best means to fight the
mosquito. In several developing countries, which host the majority of
\textit{A. aegypti} infections, anti-mosquito campaigns are carried out
inconsistently, thus it is crucial to find ways to improve the productivity of
healthcare workers in charge of these tasks. We designed a randomised field
experiment that provided individual and collective financial incentives to
healthcare agents in a Brazilian city and tested the effect of monetary rewards
on their productivity and on the number of dengue hospitalisations. We find
that financial bonuses improved the number of cleaned breeding sites in both
treatment groups (individual and team incentives) and that the collective
treatment also improved larvae extermination. The impact of our treatment on
city-level hospitalisations was not consistent across all specifications. In
sum, financial incentives may be used to boost field productivity in
anti-\textit{A. aegypti} programmes, but we suggest that further research is
required to evaluate how healthcare worker productivy impacts city-level
disease outcomes.
